Informative Oceanographic Sampling using Excursion Probabilities for Multivariate Random Fields

### 2019-05-29 main_new.tex

In our setting we study two variables; temperature and salinity, which
together characterize the phenomenon taking place in the river plume as
they define the gradients which define the frontal zone we wish to
observe. At location $\bx \in \mathcal{M} \subset \mathbf{R^2}$, we
define the two process variables by
$\bxi(\bx)=(\xi_a(\bx),\xi_b(\bx))$. %In practice there is of course time variability, but we assume this to be negligible during the AUV operation. Depth variability could also be important in some cases, but in the current application the with depths only a few meters this is considered irrelevant for mapping the phenomenon.

% In the context illustrated by Figure \ref{fig:river4},
Our focus is on spatial separation of cold freshwater from the saline
waters of the fjord and to be able to classify these water masses. In
this context, ES variability is a useful sampling criterion for guiding
the observation effort of the AUV. A bivariate ES is defined via joint
variables being below thresholds, at individual locations, for the
process over the spatial domain $\mathcal{M}$. Denoting the threshold
for temperature by $T_a$ and the threshold for salinity by $T_b$, we use
the following definition;
 \begin{equation}\label{ES}
     \mbox{ES} = \{\bx \in \mathcal{M} | \xi_a(\bx) \leq T_a,\xi_b(\bx) \leq T_b\}.
 \end{equation}
The excursions could also be defined as larger than threshold, or within a boundary of limits for the two variables. Calculations and interpretations will be similar in these different cases.

>>>>

In our setting we study two variables; temperature and salinity, which
together characterize the phenomenon taking place in the river plume as
they define the gradients defining the frontal zone. At location
$\bx \in \mathcal{M} \subset \mathbf{R^2}$, we define the two process
variables by
$\bxi(\bx)=(\xi_a(\bx),\xi_b(\bx))$. %In practice there is of course time variability, but we assume this to be negligible during the AUV operation. Depth variability could also be important in some cases, but in the current application the with depths only a few meters this is considered irrelevant for mapping the phenomenon.

% In the context illustrated by Figure \ref{fig:river4},
Our focus is on spatial separation of cold freshwater from the saline
waters of the fjord and to be able to classify these water masses. In
this context, ES variability is a useful sampling criterion for guiding
the observational effort of the AUV. A bivariate ES is defined via joint
variables \kcomment{'being below thresholds' -- is this correct?}, at
individual locations, for the process over $\mathcal{M}$. If $T_a$ is
the threshold for temperature and $T_b$ the threshold for salinity,
we use the following definition:

 \begin{equation}\label{ES}
     \mbox{ES} = \{\bx \in \mathcal{M} | \xi_a(\bx) \leq T_a,\xi_b(\bx) \leq T_b\}.
 \end{equation}

The excursions could also be defined as larger than threshold, or within a boundary of limits for the two variables. Calculations and interpretations will be similar in these different cases.
